IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/extensions.tex

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
Our formalism generalizes to a class of stateless, deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interfering at level |l|}, the
greatest lower bound of all the labels on the task labels,\footnote{
  The label on a task's current label is the current label of the
  parent at the time of creation, i.e., the initial current label of
  the task.
} i.e., they do not depends on a sensitive task's state; and, 3) make
\emph{low-progress}, i.e., if there is a task in the task list whose
label is below (or incomparable to) the label of another task, this
task (or another one at the same level) must eventually run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

More fundamentally, our scheduler parametrization is limited in being
stateless and deterministic.
%
For instance,  we do not consider  schedulers that, among other, rely
on the global state |iS| or previous task configurations, as treated
in~\cite{russo2006securing}.
%
Additionally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
(or even non-deterministic target languages) is non-trivial.
%
Such extensions may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if |l|-equivalent results are
deterministic~\cite{Zdancewic:Myers:CSFW03, sabelfeld2003language}.

>>>>

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy |alpha|, which
maps a task list to a potentially different task list, i.e.,
$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
We described two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies based on the
current task list---in fact, our formalism can be easily 
extended to consider history~\cite{BartheRRS07}.
%
As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
which always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
More precisely, our calculus generalizes to a class of deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
%greatest lower bound of all the labels on the task labels,\footnote{
%  The label on a task's current label is the current label of the
%  parent at the time of creation, i.e., the initial current label of
%  the task.
%} 
scheduling decisions on public tasks do not depend on a sensitive task's
state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
is a task in the task list whose label is below (or incomparable to) the label
of another task, this task (or another one at the same level) must eventually
run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

More fundamentally, our scheduler parametrization is limited in being
deterministic, and thus extending the system to consider non-deterministic
schedulers (or even non-deterministic target languages) is non-trivial.
%
%For instance,  we do not consider  schedulers that, among other, rely
%on the global state |iS| or previous task configurations, as treated
%in~\cite{russo2006securing}.
%
%Additionally, our definitions rely on deterministic relations,
%
Such extensions often apply security conditions which suffer 
from refinement attacks (e.g.~\cite{Smith:Volpano:MultiThreaded}) or may require to
adapt non-trivial definitions as
\emph{low-determinism}~\cite{Zdancewic:Myers:CSFW03,Huisman:Worah:Sunesen:CSFW06,Terauchi:2008},
which states that a program is secure only if |l|-equivalent results are
deterministic.
